Minimizing post-shock forecasting error using disparate information

### 2020-08-09 manuscript/comp.tex
addition of simulation results

% Created by tikzDevice version 0.12.3.1 on 2020-08-05 11:58:05
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.43,141.91) --
	( 75.27,148.65) --
	( 78.11,138.04) --
	( 80.95,120.32) --
	( 83.79,144.55) --
	( 86.63,128.04) --
	( 89.47,158.74) --
	( 92.31,142.28) --
	( 95.15,144.24) --
	( 97.99,150.16) --
	(100.83,129.86) --
	(103.67,156.20) --
	(106.51,161.19) --
	(109.35,150.66) --
	(112.19,143.27) --
	(115.03,126.88) --
	(117.87,118.05) --
	(120.71,139.15) --
	(123.55,135.40) --
	(126.40,140.74) --
	(129.24,149.36) --
	(132.08,115.48) --
	(134.92,139.71) --
	(137.76,114.03) --
	(140.60,125.67) --
	(143.44,139.07) --
	(146.28,144.69) --
	(149.12,130.89) --
	(151.96,140.09) --
	(154.80,126.64) --
	(157.64,111.23) --
	(160.48,121.82) --
	(163.32,149.80) --
	(166.16,149.85) --
	(169.00,139.78) --
	(171.84,158.01) --
	(174.68,141.87) --
	(177.52,133.42) --
	(180.36,131.05) --
	(183.20,129.40) --
	(186.04,142.69) --
	(188.88,144.63) --
	(191.72,130.06) --
	(194.56,121.56) --
	(197.41,118.55) --
	(200.25,119.73) --
	(203.09,140.14) --
	(205.93,137.20) --
	(208.77,125.79) --
	(211.61,150.02) --
	(214.45,134.16) --
	(217.29,137.62) --
	(220.13,143.96) --
	(222.97,145.02) --
	(225.81,137.14) --
	(228.65,147.61) --
	(231.49,162.41) --
	(234.33,138.41) --
	(237.17,162.38) --
	(240.01,127.19) --
	(242.85,125.12) --
	(245.69,134.60) --
	(248.53,134.89) --
	(251.37,158.83) --
	(254.21,122.69) --
	(257.05,117.16) --
	(259.89,147.80) --
	(262.73,138.62) --
	(265.57,123.35) --
	(268.42,140.39) --
	(271.26,137.29) --
	(274.10,148.46) --
	(276.94,135.80) --
	(279.78,134.54) --
	(282.62,139.54) --
	(285.46,143.03) --
	(288.30,143.37) --
	(291.14,107.15) --
	(293.98,121.09) --
	(296.82,144.70) --
	(299.66,143.32) --
	(302.50,149.80) --
	(305.34,113.62) --
	(308.18,139.96) --
	(311.02,134.15) --
	(313.86,130.85) --
	(316.70,135.42) --
	(319.54,131.11) --
	(322.38,145.18) --
	(325.22,143.55) --
	(328.06,141.15) --
	(330.90,125.31) --
	(333.74,129.29) --
	(336.59,118.52) --
	(339.43,146.06) --
	(342.27,140.93) --
	(345.11,151.97) --
	(347.95,136.60) --
	(350.79,114.01) --
	(353.63,120.33) --
	(356.47,142.22) --
	(359.31,130.73) --
	(362.15,138.80) --
	(364.99,114.92) --
	(367.83,152.60) --
	(370.67,139.26) --
	(373.51,137.13) --
	(376.35,140.56) --
	(379.19,149.07) --
	(382.03,151.38) --
	(384.87,153.12) --
	(387.71,126.88) --
	(390.55,137.55) --
	(393.39,137.71) --
	(396.23,129.83) --
	(399.07,123.04) --
	(401.91,117.89) --
	(404.75,132.35) --
	(407.60,141.10) --
	(410.44,137.00) --
	(413.28,143.73) --
	(416.12,131.05) --
	(418.96,129.54) --
	(421.80,129.16) --
	(424.64,128.38) --
	(427.48,164.19);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 67.43) -- ( 48.00,190.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 67.43) -- ( 42.00, 67.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,128.99) -- ( 42.00,128.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,190.54) -- ( 42.00,190.54);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 67.43) {-5};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,128.99) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,190.54) {5};

@@

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.43,137.81) --
	( 75.27,136.65) --
	( 78.11,143.49) --
	( 80.95,137.43) --
	( 83.79,130.64) --
	( 86.63,140.10) --
	( 89.47,133.95) --
	( 92.31,138.95) --
	( 95.15,138.13) --
	( 97.99,134.38) --
	(100.83,138.70) --
	(103.67,136.65) --
	(106.51,142.33) --
	(109.35,140.08) --
	(112.19,140.76) --
	(115.03,135.30) --
	(117.87,131.53) --
	(120.71,134.31) --
	(123.55,136.31) --
	(126.40,138.07) --
	(129.24,138.68) --
	(132.08,133.35) --
	(134.92,135.06) --
	(137.76,137.42) --
	(140.60,132.08) --
	(143.44,134.84) --
	(146.28,141.15) --
	(149.12,136.50) --
	(151.96,137.75) --
	(154.80,136.26) --
	(157.64,132.36) --
	(160.48,135.15) --
	(163.32,133.44) --
	(166.16,135.02) --
	(169.00,137.46) --
	(171.84,137.44) --
	(174.68,138.85) --
	(177.52,137.64) --
	(180.36,136.64) --
	(183.20,136.98) --
	(186.04,135.19) --
	(188.88,135.00) --
	(191.72,137.46) --
	(194.56,133.62) --
	(197.41,136.58) --
	(200.25,133.35) --
	(203.09,137.85) --
	(205.93,138.76) --
	(208.77,132.56) --
	(211.61,136.25) --
	(214.45,135.48) --
	(217.29,136.00) --
	(220.13,134.15) --
	(222.97,138.92) --
	(225.81,140.34) --
	(228.65,137.72) --
	(231.49,138.74) --
	(234.33,140.75) --
	(237.17,137.08) --
	(240.01,139.13) --
	(242.85,132.23) --
	(245.69,135.17) --
	(248.53,135.31) --
	(251.37,134.56) --
	(254.21,137.20) --
	(257.05,135.96) --
	(259.89,133.73) --
	(262.73,140.13) --
	(265.57,133.33) --
	(268.42,134.06) --
	(271.26,136.71) --
	(274.10,138.64) --
	(276.94,143.32) --
	(279.78,136.35) --
	(282.62,136.03) --
	(285.46,138.94) --
	(288.30,139.04) --
	(291.14,138.48) --
	(293.98,133.60) --
	(296.82,137.06) --
	(299.66,135.32) --
	(302.50,136.59) --
	(305.34,139.19) --
	(308.18,132.33) --
	(311.02,130.50) --
	(313.86,133.96) --
	(316.70,137.48) --
	(319.54,136.37) --
	(322.38,135.54) --
	(325.22,141.95) --
	(328.06,137.28) --
	(330.90,136.24) --
	(333.74,135.82) --
	(336.59,129.34) --
	(339.43,131.63) --
	(342.27,137.63) --
	(345.11,139.18) --
	(347.95,141.59) --
	(350.79,135.78) --
	(353.63,132.71) --
	(356.47,132.87) --
	(359.31,137.75) --
	(362.15,135.79) --
	(364.99,140.06) --
	(367.83,133.34) --
	(370.67,138.30) --
	(373.51,137.87) --
	(376.35,138.13) --
	(379.19,134.63) --
	(382.03,136.24) --
	(384.87,143.24) --
	(387.71,134.81) --
	(390.55,133.80) --
	(393.39,135.75) --
	(396.23,137.51) --
	(399.07,135.80) --
	(401.91,130.45) --
	(404.75,132.80) --
	(407.60,136.90) --
	(410.44,137.73) --
	(413.28,138.35) --
	(416.12,138.71) --
	(418.96,134.35) --
	(421.80,137.02) --
	(424.64,137.94) --
	(427.48,134.70);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 72.43,137.81) --
	( 75.27,136.65) --
	( 78.11,143.49) --
	( 80.95,137.43) --
	( 83.79,130.64) --
	( 86.63,140.10) --
	( 89.47,133.95) --
	( 92.31,138.95) --
	( 95.15,138.13) --
	( 97.99,134.38) --
	(100.83,138.70) --
	(103.67,136.65) --
	(106.51,142.33) --
	(109.35,140.08) --
	(112.19,140.76) --
	(115.03,135.30) --
	(117.87,131.53) --
	(120.71,134.31) --
	(123.55,136.31) --
	(126.40,138.07) --
	(129.24,138.68) --
	(132.08,133.35) --
	(134.92,135.06) --
	(137.76,137.42) --
	(140.60,132.08) --
	(143.44,134.84) --
	(146.28,141.15) --
	(149.12,136.50) --
	(151.96,137.75) --
	(154.80,136.26) --
	(157.64,132.36) --
	(160.48,135.15) --
	(163.32,133.44) --
	(166.16,135.02) --
	(169.00,137.46) --
	(171.84,137.44) --
	(174.68,138.85) --
	(177.52,137.64) --
	(180.36,136.64) --
	(183.20,136.98) --
	(186.04,135.19) --
	(188.88,135.00) --
	(191.72,137.46) --
	(194.56,133.62) --
	(197.41,136.58) --
	(200.25,133.35) --
	(203.09,137.85) --
	(205.93,138.76) --
	(208.77,132.56) --
	(211.61,136.25) --
	(214.45,135.48) --
	(217.29,136.00) --
	(220.13,134.15) --
	(222.97,138.92) --
	(225.81,140.34) --
	(228.65,137.72) --
	(231.49,138.74) --
	(234.33,140.75) --
	(237.17,137.08) --
	(240.01,139.13) --
	(242.85,132.23) --
	(245.69,135.17) --
	(248.53,135.31) --
	(251.37,134.56) --
	(254.21,137.20) --
	(257.05,135.96) --
	(259.89,133.73) --
	(262.73,140.13) --
	(265.57,133.33) --
	(268.42,134.06) --
	(271.26,136.71) --
	(274.10,138.64) --
	(276.94,143.32) --
	(279.78,136.35) --
	(282.62,136.03) --
	(285.46,138.94) --
	(288.30,139.04) --
	(291.14,138.48) --
	(293.98,133.60) --
	(296.82,137.06) --
	(299.66,135.32) --
	(302.50,136.59) --
	(305.34,139.19) --
	(308.18,132.33) --
	(311.02,130.50) --
	(313.86,133.96) --
	(316.70,137.48) --
	(319.54,136.37) --
	(322.38,135.54) --
	(325.22,141.95) --
	(328.06,137.28) --
	(330.90,136.24) --
	(333.74,135.82) --
	(336.59,129.34) --
	(339.43,131.63) --
	(342.27,137.63) --
	(345.11,139.18) --
	(347.95,141.59) --
	(350.79,135.78) --
	(353.63,132.71) --
	(356.47,132.87) --
	(359.31,137.75) --
	(362.15,135.79) --
	(364.99,140.06) --
	(367.83,133.34) --
	(370.67,138.30) --
	(373.51,137.87) --
	(376.35,138.13) --
	(379.19,134.63) --
	(382.03,136.24) --
	(384.87,143.24) --
	(387.71,134.81) --
	(390.55,133.80) --
	(393.39,135.75) --
	(396.23,137.51) --
	(399.07,135.80) --
	(401.91,130.45) --
	(404.75,132.80) --
	(407.60,136.90) --
	(410.44,137.73) --
	(413.28,138.35) --
	(416.12,138.71) --
	(418.96,134.35) --
	(421.80,137.02) --
	(424.64,137.94) --
	(427.48,198.96);
\definecolor{drawColor}{RGB}{0,191,255}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,189.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,212.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,176.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,201.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,198.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,181.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,229.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,197.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,187.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,197.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,197.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,187.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,203.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,166.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,196.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,183.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,165.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,179.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,169.71) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,201.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,163.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,207.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,188.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,183.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,210.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,183.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,176.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,179.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,193.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,178.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,203.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,215.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,193.21) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,158.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.68,134.70) -- (441.68,198.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.15,139.08) --
	(441.68,134.70) --
	(444.21,139.08);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-08 20:33:27
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.43,119.70) --
	( 75.27,124.71) --
	( 78.11,116.82) --
	( 80.95,103.64) --
	( 83.79,121.66) --
	( 86.63,109.38) --
	( 89.47,132.22) --
	( 92.31,119.97) --
	( 95.15,121.43) --
	( 97.99,125.83) --
	(100.83,110.73) --
	(103.67,130.32) --
	(106.51,134.04) --
	(109.35,126.21) --
	(112.19,120.71) --
	(115.03,108.51) --
	(117.87,101.94) --
	(120.71,117.64) --
	(123.55,114.85) --
	(126.40,118.83) --
	(129.24,125.24) --
	(132.08,100.04) --
	(134.92,118.06) --
	(137.76, 98.96) --
	(140.60,107.61) --
	(143.44,117.58) --
	(146.28,121.77) --
	(149.12,111.50) --
	(151.96,118.34) --
	(154.80,108.34) --
	(157.64, 96.87) --
	(160.48,104.75) --
	(163.32,125.56) --
	(166.16,125.60) --
	(169.00,118.11) --
	(171.84,131.67) --
	(174.68,119.66) --
	(177.52,113.38) --
	(180.36,111.62) --
	(183.20,110.39) --
	(186.04,120.28) --
	(188.88,121.72) --
	(191.72,110.88) --
	(194.56,104.55) --
	(197.41,102.32) --
	(200.25,103.20) --
	(203.09,118.38) --
	(205.93,116.19) --
	(208.77,107.70) --
	(211.61,125.73) --
	(214.45,113.93) --
	(217.29,116.50) --
	(220.13,121.22) --
	(222.97,122.01) --
	(225.81,116.15) --
	(228.65,123.94) --
	(231.49,134.95) --
	(234.33,117.09) --
	(237.17,134.93) --
	(240.01,108.75) --
	(242.85,107.21) --
	(245.69,114.25) --
	(248.53,114.47) --
	(251.37,132.28) --
	(254.21,105.40) --
	(257.05,101.28) --
	(259.89,124.08) --
	(262.73,117.25) --
	(265.57,105.89) --
	(268.42,118.56) --
	(271.26,116.26) --
	(274.10,124.57) --
	(276.94,115.15) --
	(279.78,114.21) --
	(282.62,117.93) --
	(285.46,120.53) --
	(288.30,120.78) --
	(291.14, 93.84) --
	(293.98,104.20) --
	(296.82,121.77) --
	(299.66,120.74) --
	(302.50,125.57) --
	(305.34, 98.65) --
	(308.18,118.24) --
	(311.02,113.92) --
	(313.86,111.47) --
	(316.70,114.87) --
	(319.54,111.66) --
	(322.38,122.13) --
	(325.22,120.92) --
	(328.06,119.13) --
	(330.90,107.34) --
	(333.74,110.31) --
	(336.59,102.29) --
	(339.43,122.78) --
	(342.27,118.97) --
	(345.11,127.18) --
	(347.95,115.75) --
	(350.79, 98.94) --
	(353.63,103.64) --
	(356.47,119.92) --
	(359.31,111.38) --
	(362.15,117.39) --
	(364.99, 99.61) --
	(367.83,127.65) --
	(370.67,117.72) --
	(373.51,116.14) --
	(376.35,118.69) --
	(379.19,125.02) --
	(382.03,126.74) --
	(384.87,128.03) --
	(387.71,108.51) --
	(390.55,116.45) --
	(393.39,116.57) --
	(396.23,110.71) --
	(399.07,105.66) --
	(401.91,101.83) --
	(404.75,112.58) --
	(407.60,119.09) --
	(410.44,116.04) --
	(413.28,121.05) --
	(416.12,111.62) --
	(418.96,110.49) --
	(421.80,110.21) --
	(424.64,109.63) --
	(427.48,182.07);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,252.94);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 64.28) -- ( 48.00,201.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00, 64.28) -- ( 42.00, 64.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,110.08) -- ( 42.00,110.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,155.88) -- ( 42.00,155.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 48.00,201.67) -- ( 42.00,201.67);

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60, 64.28) {-5};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,110.08) {0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,155.88) {5};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at ( 33.60,201.67) {10};

@@

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.43,116.65) --
	( 75.27,115.78) --
	( 78.11,120.87) --
	( 80.95,116.36) --
	( 83.79,111.31) --
	( 86.63,118.35) --
	( 89.47,113.78) --
	( 92.31,117.49) --
	( 95.15,116.88) --
	( 97.99,114.09) --
	(100.83,117.31) --
	(103.67,115.79) --
	(106.51,120.01) --
	(109.35,118.34) --
	(112.19,118.84) --
	(115.03,114.78) --
	(117.87,111.97) --
	(120.71,114.04) --
	(123.55,115.53) --
	(126.40,116.84) --
	(129.24,117.29) --
	(132.08,113.33) --
	(134.92,114.60) --
	(137.76,116.36) --
	(140.60,112.38) --
	(143.44,114.43) --
	(146.28,119.13) --
	(149.12,115.67) --
	(151.96,116.60) --
	(154.80,115.49) --
	(157.64,112.59) --
	(160.48,114.67) --
	(163.32,113.39) --
	(166.16,114.57) --
	(169.00,116.38) --
	(171.84,116.37) --
	(174.68,117.42) --
	(177.52,116.52) --
	(180.36,115.78) --
	(183.20,116.03) --
	(186.04,114.70) --
	(188.88,114.55) --
	(191.72,116.39) --
	(194.56,113.53) --
	(197.41,115.73) --
	(200.25,113.33) --
	(203.09,116.67) --
	(205.93,117.35) --
	(208.77,112.74) --
	(211.61,115.48) --
	(214.45,114.91) --
	(217.29,115.30) --
	(220.13,113.92) --
	(222.97,117.48) --
	(225.81,118.53) --
	(228.65,116.58) --
	(231.49,117.34) --
	(234.33,118.84) --
	(237.17,116.11) --
	(240.01,117.63) --
	(242.85,112.50) --
	(245.69,114.69) --
	(248.53,114.79) --
	(251.37,114.23) --
	(254.21,116.19) --
	(257.05,115.27) --
	(259.89,113.61) --
	(262.73,118.37) --
	(265.57,113.31) --
	(268.42,113.85) --
	(271.26,115.83) --
	(274.10,117.26) --
	(276.94,120.74) --
	(279.78,115.56) --
	(282.62,115.32) --
	(285.46,117.49) --
	(288.30,117.56) --
	(291.14,117.14) --
	(293.98,113.51) --
	(296.82,116.09) --
	(299.66,114.80) --
	(302.50,115.74) --
	(305.34,117.67) --
	(308.18,112.57) --
	(311.02,111.21) --
	(313.86,113.78) --
	(316.70,116.40) --
	(319.54,115.57) --
	(322.38,114.95) --
	(325.22,119.73) --
	(328.06,116.25) --
	(330.90,115.48) --
	(333.74,115.16) --
	(336.59,110.34) --
	(339.43,112.05) --
	(342.27,116.51) --
	(345.11,117.67) --
	(347.95,119.46) --
	(350.79,115.14) --
	(353.63,112.85) --
	(356.47,112.97) --
	(359.31,116.60) --
	(362.15,115.14) --
	(364.99,118.32) --
	(367.83,113.32) --
	(370.67,117.01) --
	(373.51,116.69) --
	(376.35,116.89) --
	(379.19,114.28) --
	(382.03,115.47) --
	(384.87,120.69) --
	(387.71,114.41) --
	(390.55,113.66) --
	(393.39,115.12) --
	(396.23,116.42) --
	(399.07,115.15) --
	(401.91,111.17) --
	(404.75,112.92) --
	(407.60,115.97) --
	(410.44,116.59) --
	(413.28,117.05) --
	(416.12,117.32) --
	(418.96,114.07) --
	(421.80,116.06) --
	(424.64,116.75) --
	(427.48,114.33);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 72.43,116.65) --
	( 75.27,115.78) --
	( 78.11,120.87) --
	( 80.95,116.36) --
	( 83.79,111.31) --
	( 86.63,118.35) --
	( 89.47,113.78) --
	( 92.31,117.49) --
	( 95.15,116.88) --
	( 97.99,114.09) --
	(100.83,117.31) --
	(103.67,115.79) --
	(106.51,120.01) --
	(109.35,118.34) --
	(112.19,118.84) --
	(115.03,114.78) --
	(117.87,111.97) --
	(120.71,114.04) --
	(123.55,115.53) --
	(126.40,116.84) --
	(129.24,117.29) --
	(132.08,113.33) --
	(134.92,114.60) --
	(137.76,116.36) --
	(140.60,112.38) --
	(143.44,114.43) --
	(146.28,119.13) --
	(149.12,115.67) --
	(151.96,116.60) --
	(154.80,115.49) --
	(157.64,112.59) --
	(160.48,114.67) --
	(163.32,113.39) --
	(166.16,114.57) --
	(169.00,116.38) --
	(171.84,116.37) --
	(174.68,117.42) --
	(177.52,116.52) --
	(180.36,115.78) --
	(183.20,116.03) --
	(186.04,114.70) --
	(188.88,114.55) --
	(191.72,116.39) --
	(194.56,113.53) --
	(197.41,115.73) --
	(200.25,113.33) --
	(203.09,116.67) --
	(205.93,117.35) --
	(208.77,112.74) --
	(211.61,115.48) --
	(214.45,114.91) --
	(217.29,115.30) --
	(220.13,113.92) --
	(222.97,117.48) --
	(225.81,118.53) --
	(228.65,116.58) --
	(231.49,117.34) --
	(234.33,118.84) --
	(237.17,116.11) --
	(240.01,117.63) --
	(242.85,112.50) --
	(245.69,114.69) --
	(248.53,114.79) --
	(251.37,114.23) --
	(254.21,116.19) --
	(257.05,115.27) --
	(259.89,113.61) --
	(262.73,118.37) --
	(265.57,113.31) --
	(268.42,113.85) --
	(271.26,115.83) --
	(274.10,117.26) --
	(276.94,120.74) --
	(279.78,115.56) --
	(282.62,115.32) --
	(285.46,117.49) --
	(288.30,117.56) --
	(291.14,117.14) --
	(293.98,113.51) --
	(296.82,116.09) --
	(299.66,114.80) --
	(302.50,115.74) --
	(305.34,117.67) --
	(308.18,112.57) --
	(311.02,111.21) --
	(313.86,113.78) --
	(316.70,116.40) --
	(319.54,115.57) --
	(322.38,114.95) --
	(325.22,119.73) --
	(328.06,116.25) --
	(330.90,115.48) --
	(333.74,115.16) --
	(336.59,110.34) --
	(339.43,112.05) --
	(342.27,116.51) --
	(345.11,117.67) --
	(347.95,119.46) --
	(350.79,115.14) --
	(353.63,112.85) --
	(356.47,112.97) --
	(359.31,116.60) --
	(362.15,115.14) --
	(364.99,118.32) --
	(367.83,113.32) --
	(370.67,117.01) --
	(373.51,116.69) --
	(376.35,116.89) --
	(379.19,114.28) --
	(382.03,115.47) --
	(384.87,120.69) --
	(387.71,114.41) --
	(390.55,113.66) --
	(393.39,115.12) --
	(396.23,116.42) --
	(399.07,115.15) --
	(401.91,111.17) --
	(404.75,112.92) --
	(407.60,115.97) --
	(410.44,116.59) --
	(413.28,117.05) --
	(416.12,117.32) --
	(418.96,114.07) --
	(421.80,116.06) --
	(424.64,116.75) --
	(427.48,207.97);
\definecolor{drawColor}{RGB}{0,191,255}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,201.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,218.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,191.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,207.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,194.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,230.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,213.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,213.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,199.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,207.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,215.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,207.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,198.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,211.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,184.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,206.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,196.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,183.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,193.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,186.22) circle (  2.25);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,213.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,209.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,181.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,214.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,200.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,196.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,216.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,196.21) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,191.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,193.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,203.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,192.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,211.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,220.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,203.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,178.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (421.80,215.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (436.00,114.33) -- (436.00,207.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.47,118.72) --
	(436.00,114.33) --
	(438.53,118.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.53,203.59) --
	(436.00,207.97) --
	(433.47,203.59);
